\documentclass{article}
\usepackage[hmargin=1.25in,vmargin=1in]{geometry}
\usepackage{graphicx}
\usepackage[colorlinks=true,bookmarks=true,bookmarksnumbered=true]{hyperref}

\title{SEU History}
\author{Sparky\_14145}

\begin{document}
    \maketitle

    Southeast University is a university with a long history. Dating back to 1903,
    Sanjiang Normal School is the origin of Southeast University. As one of the
    earliest modern higher school, Sanjiang Normal School not only carried Chinese wish
    to be alive, to be knowledgable, and to be strong, but also was a pioneer in the way
    of the modernization of Chinese education. In 1915, Sanjiang Normal School was changed
    into Nanjing Higher Normal School, which was one of the earliest six national higher
    normal schools. In 1920, Nanjing Higher Normal School expanded what it teached and
    researched, which made it a simple university in fact. National Southeast University was
    the third name Southeast University had had. As one of the earliest national
    universities, National Southeast University had the widest range of classes
    and professions, practicing ``to educate the three parts of education'' and initiating
    ``to maintain the four balances''. After a short time using National Fourth Zhongshan
    University and Jiangsu University as name, National Southeast University became
    National Central University, with eight colleges and fifty-five departments were set.
    Then, People's Republic of China was born, and National Central University became
    Nanjing University. After that, Nanjing University was split apart into many institutes,
    and Nanjing Institute of Technology, a part of the split Nanjing University, finally
    became Southeast University. Today Southeast University is still in a fast development,
    serving more and more excellent talents to the community. From minerals exploiting,
    to material crafting and application, from semiconductor devices, to mobile communication,
    we can see contributions made by SEUers everywhere.
\end{document}