\documentclass{article}
\usepackage{xeCJK}
\usepackage[hmargin=1.25in,vmargin=1in]{geometry}
\usepackage{graphicx}
\usepackage[colorlinks=true,bookmarks=true,bookmarksnumbered=true]{hyperref}

\title{Presenation Outline: College of Software Engineering}
\author{71120226 陈宇轩\\71120205 程建涛}

\begin{document}
    \maketitle

    \paragraph{Topic} Introducing CoSE of Southeast University.
    \paragraph{Presentation purpose} To raise some high school graduates' interest to
    SEU.
    \paragraph{Thesis statement} It is a good idea to learn CoSE in SEU.

    \section{Introduction}

    We know Southeast University (SEU) is one of the national key universities administered
    directly under the Ministry of Education of China. Its College of Software Engineering
    (CoSE), as one of 35 national pilot software schools, has been founded in December 2001
    and started its undergraduate program and postgraduate program in the field of software
    engineering, authorized by Ministry of Education and former State Development and Planning
    Committee. Carrying the idea of “Pursuing Excellence”, CoSE insists on the concepts of
    reformation of education, normalization of administration, and creation and innovation in
    science and technology, integrates the sound resources and advantages of the university in
    the discipline of computer science, mathematics, telecommunications, IC design and engineering.
    After five years commitment, CoSE has formed the pedagogical model of combining class teaching
    with case study, strongthened foreign language learning through international academic
    exchange, increased employment through learning by doing, advanced the discipline through
    effective human resource management. CoSE has committed to provide quality professional
    education to produce high level software talents with the capability of creative and innovative,
    cross-discipline knowledge base, challenging international competition.

    \section{Body}
    \subsection{Main point: CoSE of SEU is highly developed}

    \begin{enumerate}
        \item CoSE of SEU is active in education reformation. Based on futures of Software Engineering,
        referencing to IEEE/ACM CC2001, SWEBOK, SE2004 and CCSE2004 standards, course sysytem of CoSE
        aims at making the students command the latest technologies as well as meeting the
        requirements of IT companies. 
        \item CoSE of SEU is highly rewarded. In 2007, CoSE was rewarded as ``Software Engineering
        Postgraduate Joint Training Demonstration Base''. Software Engineering and Network Engineering
        were accepted as Specialized Professional Construction Point. Data Structure and Introduction
        to Physics were included in 100 Bilingual Teaching Demonstration Courses.
        \item CoSE of SEU is internationally communicated. CoSE had mutl-dimensional communications and
        cooperations with corporations like Microsoft, IBM, Ericsson, HP, Cisco, Oracle, Intel, Motorola,
        Trend Micro, Lenovo, ZTE, Huawei, etc., setting up lots of practice bases and united laboratories.
        Some of them even had participated in student education works.
    \end{enumerate}

    \subsection{Main point: Students of SEU CoSE are widely welcomed}

    \begin{enumerate}
        \item Famous IT companies accept the graduates from SEU CoSE. About fifty percent of graduates
        works in great IT companies including IBM, Intel, SAP, Alibaba, Tencent, Baidu and Huawei. Most
        of them work on software desinging, researching, developing, applicating, referencing, project
        management, quality guaranting, etc., and get highly prised by the employers.
        \item Famous universities acceot the graduates from SEU CoSE. 
    \end{enumerate}

    \subsection{Main point: Students of SEU CoSE have beautiful university lives}

    \begin{enumerate}
        \item Many competitions are avaliable. Students of SEU CoSE had participated in many competitions
        like The Challenge Cup, National College Students Software Innovation Competition, Contemporary
        Undergraduate Mathematical Contest in Modeling (CUMCM), International Collegiate Programming Contest
        (ICPC a.k.a. ACM/ICPC), etc., winning good prizes.
        \item Many communties are avaliable. More than one hundred communties like Microsoft Students' Club
        (MSC), SiliCOM Computer Repairing Community, Robot Club, Comics and Animation Club, etc, are avaliable.
        There is also a great event, called ``War of Hundred Communties'', where you can learn almost everything
        about all the communties.
    \end{enumerate}

    \section{Conclusion}

    To high school graduates, it is a nice choice to learn Software Engineering in Southeast University. SEU CoSE
    provides students a platform to show abilities out, to learn knowledge and skills, and to reach high
    quality education. But life in SEU is not boring. Instead, it is colorful and enjoyable, since many activities
    are served to everyone!
\end{document}